---
output:
  word_document: default
  html_document: default
---
```{r}
library("tidyverse")
```

```{r}
diamonddata=diamonds
summarize(diamonddata)
NROW(diamonddata)
NCOL(diamonddata)
summary(diamonddata)
```

# 53,940 ROWS AND 10 COLUMNS



```{r}
ggplot(data = diamonddata, aes(x = carat,y = price, label = color))+
geom_point()+ 
  labs (title = "Plot of Cost per Carat", x = "Carat", y = "Price", color = "carat")+
  scale_y_continuous(name="Price (in $)", labels = scales::comma)

```
# From above sctterplot I observe that as the carat size goes up so does the cost of the carat.

```{r}
ggplot(data = diamonddata, aes(x = carat,y = price, label = cut, color = cut))+
geom_point()+ 
  labs (title = "Plot of Cost per Carat", x = "Carat", y = "Price", color = "cut")+
  scale_y_continuous(name="Price (in $)", labels = scales::comma)

```


# As per the plot above I can observe that as the prices go up so does the type of cut and the size of the carat


```{r}
ggplot(data = diamonddata, aes(x = carat,y = price, label = cut, color = cut))+
geom_point()+ 
  labs (title = "Plot of Cost per Carat", x = "Carat", y = "Price", color = "cut")+
  facet_wrap(~color)+
  scale_y_continuous(name="Price (in $)", labels = scales::comma)
```

# From plot above I observe that as the cut that is very good and premium has higher prices and higher carat sizes too.

```{r}
library(readr)
InventoryData <- read_csv("InventoryData.csv")
View(InventoryData)
inventory<-InventoryData
view(inventory)
```



```{r}
summary(inventory)
```

```{r}
inventoryA<-inventory %>%
  select(`Item SKU`, Supplier, `Cost per Unit ($)`, `On Hand`, `Annual Demand`)
```
# 13561 rows in this new dataset

```{r}
inventoryA = mutate(inventoryA, OnHandRatio = `On Hand` / `Annual Demand`)
```

# The code above creates a new variable called OnHandRatio that is a result of On Hand divided by Annual Demand

```{r}
inventoryA<-inventoryA %>%
rename(x = `Cost per Unit ($)`)
```



## Below is my R code for task 9. I wasn’t able to add it to the rmd file as it wouldn’t knit to word with an error. Hate to lose that point but I tried everything including renaming the Cost per Unit ($) variable because I thought the dollar sign was a problem 

## avg_cost<-inventoryA %>%
##    summarize(SKUAvgCost = mean(x)) %>%
##    mutate(SKUAvgCost = mean(x) / `Item SKU`) %>%
##  select(`SKUAvgCost`, `Item SKU`)

## I find these concepts quite challenging to me; mutate, arrange, select, group_by etc. and the formatting of a plot so its easier to read. One step at a time though.
